### 2024-02-09 paper_sisc_first_revision/localpsf.tex
update ellipsoid width illustration. Work on blur section

\section{Preliminaries}

>>>>

\section{Overview of the method and illustration on a blur operator}

Before delving into technical details, we provide an overview of the method. Along the way, we illustrate steps using a spatially variant blur example, in which the integral kernel is given as follows:
$$\Phi(y,x) = (1 - a f(y,x)) g(x) \exp \left(-\frac{1}{2}h^T(y,x) C^{-1} h(y,x)\right).$$ 
Here, $h(y,x) = R(\theta(x)) (y-x)$, $R(\theta(x))$ is the 2D rotation matrix by angle $\theta(x) = (x^1 + x^2) \pi / 2$, $C = L^2 \operatorname{diag}(c_1, c_2)$, $g(x) = x^1(1-x^1)x^2(1-x^2)$,  and $f(x,y) = \cos\left(p^1(y,x) / \sqrt{c_1 / 2.0}\right) \sin\left(p^2(y,x) / \sqrt{c_2 / 2.0}\right)$ for some constants $a, L, c_1, c_2$. In this section we use $a=1.0$, $L^2=1.0$, $c_1=0.01$, and $c_2=0.0025$. Using this kernel, the impulse response $\phi_x$ is a bumpy blob that is centered near $x$, and is rotated and scaled in a manner that depends on $x$ (see Figure \ref{fig:frog1}). Note that for this operator, using our method is unnecessary because entries of the kernel are given directly via a formula. The purpose of this example is to illustrate the method using an operator which is known exactly and may be easily visualized.

%The constant $L$ controls how wide the blob is, and $a$ controls the bumpiness. With $a=0$, $\phi_x$ is a Gaussian. As $a$ increases, $\phi_x$ becomes more bumpy. When $a > 1$, the integral kernel contains negative values, which violates the assumptions of our method. In the numerical results section we will vary $a$ and $L$, even allowing $a>1$ to test the robustness of the method to violations of the non-negative kernel assumption.

\begin{figure}
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[scale=0.2]{kernel_impulse_illustration2.pdf}
		\caption{Kernel and impulse responses}
		\label{fig:kernel_impulse_illustration}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[scale=0.4]{frog_ellipsoid_width2.pdf}
		\caption{Impulse response support ellipsoid}
		\label{fig:frog_ellipsoid_width}
	\end{subfigure}

	\caption{(\ref{fig:kernel_impulse_illustration}) asdf. \ref{fig:frog_ellipsoid_width}) asdf2
	}
	\label{fig:frog1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=0.2]{frog_moments2.pdf}	
	\caption{asdf3
	}
	\label{fig:frog2}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=0.25]{frog_batches2.pdf}	
	\caption{asdf4
	}
	\label{fig:frog3}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=0.2]{frog_hmatrix_knn_impulse2.png}	
	\caption{asdfg
	}
	\label{fig:frog4}
\end{figure}

\begin{figure}
	\begin{subfigure}[b]{0.30\textwidth}
		\centering
		\includegraphics[scale=0.35]{frog_column_errors_psf5.png}
		\caption{PSF(5)}
		\label{fig:blur_error_psf5}
	\end{subfigure}
	\begin{subfigure}[b]{0.30\textwidth}
		\centering
		\includegraphics[scale=0.35]{frog_column_errors_psf10.png}
		\caption{PSF(10)}
		\label{fig:blur_error_psf10}
	\end{subfigure}
	\begin{subfigure}[b]{0.37\textwidth}
		\centering
		\includegraphics[scale=0.35]{frog_column_errors_psf20_colorbar.png}
		\caption{PSF(20)}
		\label{fig:blur_error_psf20}
	\end{subfigure}

	\caption{columnwise error plots for kernel reconstruction
	}
	\label{fig:frog5}
\end{figure}

\section{Technical preliminaries}
